---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
treat_age_sex <- treat_age_sex %>% 
  clean_names()

head(treat_age_sex)
```

__Hypotheses__

H0: There is no significant difference in the mean stay of elective inpatients
and emergency inpatients.

$$H_0: \mu_{elective\ stay} - \mu_{emergency\ stay} = 0$$

Ha: There is a significant difference in the mean stay of elective inpatients
and emergency inpatients

$$H_A: \mu_{elective\ stay} - \mu_{emergency\ stay} \neq 0$$


```{r}
hyp_data <- treat_age_sex %>% 
  select(admission_type, average_length_of_stay)

hyp_data_no_na <- hyp_data %>% 
  filter(!is.na(average_length_of_stay))

hyp_data_no_na %>% 
  distinct(admission_type)

my_data <- hyp_data_no_na %>% 
  filter(admission_type %in% c("Elective Inpatients", "Emergency Inpatients"))

library(infer)
observed_stat <- my_data %>% 
  specify(average_length_of_stay~admission_type) %>% 
  calculate(stat = "diff in means", order = c("Elective Inpatients", "Emergency Inpatients"))

observed_stat

# emergency inpatients stay longer on average 3.36 days
```
```{r}
null_distribution <- my_data %>% 
  specify(average_length_of_stay~admission_type) %>% 
  hypothesise(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Elective Inpatients", "Emergency Inpatients"))

null_distribution %>% 
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "left")

null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "left")
```

__Interpretation__

Alpha = 0.05

Since our p-value of 0.000... < 0.05, we reject the null hypothesis that there
is no statistically significant difference in the mean length of stay between
elective and emergency inpatients. 